Comparative vaccine effectiveness of ChAdOx1 versus BNT162b2 in Health and Social Care workers in England: Supplementary materials

### 2021-09-09 analysis/report/draft-supplement.Rmd
fix mapping

    cmlinc %>%
      filter(model == modell) %>%
      ggplot(cmlinc)+
      geom_step(aes(x=tstop, y=(1-survival)*1000, group=vax1_az_descr, colour=vax1_az_descr))+
      geom_rect(aes(xmin=lag(tstop, 1, 0), xmax=tstop, ymin=(1-survival.ll)*1000, ymax=(1-survival.ul)*1000, group=vax1_az_descr, fill=vax1_az_descr), alpha=0.1)+
      geom_hline(aes(yintercept=0), colour='black')+
      facet_grid(cols=vars(outcome_descr))+
      scale_x_continuous(
        breaks = seq(0,7*52,by=14),
        expand = expansion(0)
      )+
      scale_y_continuous(
        expand = expansion(0),
        limits = c(0L,NA)
      )+
      scale_colour_brewer(type="qual", palette="Set1", na.value="grey")+
      scale_fill_brewer(type="qual", palette="Set1", guide="none", na.value="grey")+
      labs(
        x=NULL,
        y="Marginalised cumulative incidence\nper 1000",
        colour=NULL
      )+
      theme_minimal()+
      theme(
        legend.position=c(0.1,0.95),
        legend.justification = c(0,1),
        legend.direction = "vertical",
        axis.text.x.top=element_text(hjust=0),

@@

    hazard %>% 
      filter(model == modell) %>%
      ggplot()+
      geom_hline(aes(yintercept=1), colour='black')+
      geom_line(aes(x=tstop, y=hr), colour='orchid4')+
      geom_ribbon(aes(x=tstop, ymin=hr.ll, ymax=hr.ul), alpha=0.1, colour="transparent", fill='orchid4')+
      facet_grid(cols=vars(outcome_descr))+
      scale_x_continuous(
        limits = c(0, NA),
        breaks = seq(0,7*52,by=14),
        expand = expansion(0)
      )+
      scale_y_log10(
        #breaks=c(0.125, 0.167, 0.25, 0.333, 0.5, 0.667, 1, 1.5, 2, 3, 4, 6, 8),
        sec.axis = dup_axis(name="Lower hazard after \n <- BNT162b2 / ChAdOx1 ->", breaks = NULL)
      )+
      coord_cartesian(ylim= c(0.1, 10))+
      labs(
        x = "Days since first dose",
        y = "Hazard ratio"
      )+
      theme_bw()+
      theme(
        panel.border = element_blank(),
        axis.line.y.left = element_line(colour = "black"),

@@

    modell <- model
    riskdiff %>%
      filter(model==modell) %>%
      ggplot(riskdiff)+
      geom_hline(aes(yintercept=0), colour='black')+
      geom_step(aes(x=tstop, y=diff*1000), colour='orchid4')+
      geom_rect(aes(xmin=lag(tstop, 1, 0), xmax=tstop, ymin=diff.ll*1000, ymax=diff.ul*1000), alpha=0.1, colour="transparent", fill='orchid4')+
      facet_grid(cols=vars(outcome_descr))+
      scale_x_continuous(
        limits = c(0, NA),
        breaks = seq(0,7*52,by=14),
        expand = expansion(0)
      )+
      scale_y_continuous(
        expand = expansion(0),
        sec.axis = dup_axis(name="Lower risk after \n <- BNT162b2 / ChAdOx1 ->", breaks = NULL)
      )+
      coord_cartesian(ylim= c(-5, 5))+
      scale_colour_brewer(type="qual", palette="Set1", na.value="grey")+
      scale_fill_brewer(type="qual", palette="Set1", guide="none", na.value="grey")+
      labs(
        x=NULL,
        y="Difference\nin cumulative incidence\nper 1000",
        colour=NULL
      )+
      theme_bw()+
      theme(
        panel.border = element_blank(),
        axis.line.y.left = element_line(colour = "black"),

>>>>

    cmlinc %>%
      filter(model == modell) %>%
      ggplot()+
      geom_step(aes(x=tstop, y=(1-survival)*1000, group=vax1_az_descr, colour=vax1_az_descr))+
      geom_rect(aes(xmin=lag(tstop, 1, 0), xmax=tstop, ymin=(1-survival.ll)*1000, ymax=(1-survival.ul)*1000, group=vax1_az_descr, fill=vax1_az_descr), alpha=0.1)+
      geom_hline(aes(yintercept=0), colour='black')+
      facet_grid(cols=vars(outcome_descr))+
      scale_x_continuous(
        breaks = seq(0,7*52,by=28),
        expand = expansion(0)
      )+
      scale_y_continuous(
        expand = expansion(0),
        limits = c(0L,NA)
      )+
      scale_colour_brewer(type="qual", palette="Set1", na.value="grey")+
      scale_fill_brewer(type="qual", palette="Set1", guide="none", na.value="grey")+
      labs(
        x=NULL,
        y="Marginalised cumulative incidence\nper 1000",
        colour=NULL
      )+
      theme_minimal()+
      theme(
        legend.position=c(0.1,0.95),
        legend.justification = c(0,1),
        legend.direction = "vertical",
        axis.text.x.top=element_text(hjust=0),

@@

    hazard %>% 
      filter(model == modell) %>%
      ggplot()+
      geom_hline(aes(yintercept=1), colour='black')+
      geom_line(aes(x=tstop, y=hr), colour='orchid4')+
      geom_ribbon(aes(x=tstop, ymin=hr.ll, ymax=hr.ul), alpha=0.1, colour="transparent", fill='orchid4')+
      facet_grid(cols=vars(outcome_descr))+
      scale_x_continuous(
        limits = c(0, NA),
        breaks = seq(0,7*52,by=28),
        expand = expansion(0)
      )+
      scale_y_log10(
        #breaks=c(0.125, 0.167, 0.25, 0.333, 0.5, 0.667, 1, 1.5, 2, 3, 4, 6, 8),
        sec.axis = dup_axis(name="Lower hazard after \n <- BNT162b2 / ChAdOx1 ->", breaks = NULL)
      )+
      coord_cartesian(ylim= c(0.1, 10))+
      labs(
        x = "Days since first dose",
        y = "Hazard ratio"
      )+
      theme_bw()+
      theme(
        panel.border = element_blank(),
        axis.line.y.left = element_line(colour = "black"),

@@

    modell <- model
    riskdiff %>%
      filter(model==modell) %>%
      ggplot()+
      geom_hline(aes(yintercept=0), colour='black')+
      geom_step(aes(x=tstop, y=diff*1000), colour='orchid4')+
      geom_rect(aes(xmin=lag(tstop, 1, 0), xmax=tstop, ymin=diff.ll*1000, ymax=diff.ul*1000), alpha=0.1, colour="transparent", fill='orchid4')+
      facet_grid(cols=vars(outcome_descr))+
      scale_x_continuous(
        limits = c(0, NA),
        breaks = seq(0,7*52,by=28),
        expand = expansion(0)
      )+
      scale_y_continuous(
        expand = expansion(0),
        sec.axis = dup_axis(name="Lower risk after \n <- BNT162b2 / ChAdOx1 ->", breaks = NULL)
      )+
      coord_cartesian(ylim= c(-5, 5))+
      scale_colour_brewer(type="qual", palette="Set1", na.value="grey")+
      scale_fill_brewer(type="qual", palette="Set1", guide="none", na.value="grey")+
      labs(
        x=NULL,
        y="Difference\nin cumulative incidence\nper 1000",
        colour=NULL
      )+
      theme_bw()+
      theme(
        panel.border = element_blank(),
        axis.line.y.left = element_line(colour = "black"),
